### 2018-12-18 Sections/network_topologies.tex

We will now review some of the graph structures most likely to arise in quantum networks, learning from the structures that have become ubiquitous in classical networking.

A summary of the mathematical characteristics of the topologies presented is shown in Table.~\ref{tab:net_top_sum}.\comment{Finish this text - expand on why these properties matter}

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		Topology & Vertices ($|V|$) & Edges ($|E|$) & Diameter ($d$) \\
      	\hline
      	\hline
      	Point-to-point & $2$ & $1$ & $1$ \\
      	Linear & $|V|$ & \mbox{$O(|V|)$} & \mbox{$O(|V|)$} \\
      	Complete & $|V|$ & \mbox{$O(|V|^2)$} & $1$ \\
      	Lattice & $mn$ & \mbox{$O(mn)$} & \mbox{$O(m+n)$} \\
      	Tree & $|V|$ & \mbox{$O(|V|)$} & \mbox{$O(\log |V|)$} \\
      	Percolation & \mbox{$O(p_\mathrm{vertex}\cdot |V|)$} & \mbox{$O(p_\mathrm{edge}\cdot |E|)$} & variable \\
      	Random & \mbox{$O(p_\mathrm{vertex}\cdot |V|)$} & \mbox{$O(p_\mathrm{edge}\cdot |V|^2)$} & variable \\
      	Scale-free & $|V|$ & $|E|$ & \mbox{$O(\log\log |V|)$}\\
      	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of the mathematical characteristics of different network topologies.} \label{tab:net_top_sum}
\end{table*}
\startalgtable

@@

\comment{To do}

@@

We refer to a random graph as being one in which edges between each pair of vertices occur with some probability $p_\mathrm{edge}$. No vertices are removed from the network, although some may have order \mbox{$|v|=0$}, i.e \mbox{$p_\mathrm{vertex}=1$}. This can be thought of as the edge percolation graph of the complete graph $K_{|V|}$. Some examples are shown in Fig.~\ref{fig:random_graph}.

\comment{Show average edge and vertex numbers}

>>>>

We will now review some of the graph structures most likely to arise in quantum networks, learning from the structures that have become ubiquitous in classical networking. Understanding the basic mathematical properties of these different network topologies is extremely important to take into consideration when designing future quantum networks, since they strongly impact important features such as construction cost of the network infrastructure, routing cost vector analysis (Sec.~\ref{sec:quantum_meas_cost}), likelihood of successful routing, and transmission time.

A summary of the basic mathematical characteristics of the topologies presented is shown in Table.~\ref{tab:net_top_sum}, specifically showing the number of edges and vertices, the \textit{diameter} of the topologies (i.e the distance between extremal points in the network).

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		Topology & Vertices ($|V|$) & Edges ($|E|$) & Diameter ($d$) \\
      	\hline
      	\hline
      	Point-to-point & $2$ & $1$ & $1$ \\
      	Linear & $|V|$ & \mbox{$O(|V|)$} & \mbox{$|V|$} \\
      	Complete & $|V|$ & \mbox{$O(|V|^2)$} & $1$ \\
      	Lattice & $mn$ & \mbox{$O(mn)$} & \mbox{$O(m+n)$} \\
      	Tree & $|V|$ & \mbox{$O(|V|)$} & \mbox{$O(\log |V|)$} \\
      	Percolation & \mbox{$p_\mathrm{vertex}\cdot |V|$} & \mbox{$p_\mathrm{edge}\cdot |E|$} & variable \\
      	Random & \mbox{$p_\mathrm{vertex}\cdot |V|$} & \mbox{$p_\mathrm{edge}\cdot O(|V|^2)$} & variable \\
      	Scale-free & $|V|$ & $|E|$ & \mbox{$O(\log\log |V|)$}\\
      	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of the mathematical characteristics of different network topologies.} \label{tab:net_top_sum}
\end{table*}
\startalgtable

@@

A linear graph topology, shown in Fig.~\ref{fig:linear_graph}, has very simple properties. The number of edges simply scales as,
\begin{align}
|E|=|V|-1,	
\end{align}
and the graph diameter is simply the number of vertices,
\begin{align}
d = |V|.	
\end{align}
There are limited routing considerations for such a topology since there is always exactly one route between two points, although buffering issues may still arise under congestion.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{linear_graph}
\caption{A simple linear graph topology with \mbox{$|V|=10$} vertices.}\label{fig:linear_graph}
\end{figure}

Because there is no path redundancy, linear graphs are vulnerable to node failures, since the deletion of a since node makes disconnects the network.

@@

We refer to a random graph as being one in which edges between each pair of vertices occur with some probability $p_\mathrm{edge}$. No vertices are removed from the network, although some may have order \mbox{$|v|=0$}, i.e \mbox{$p_\mathrm{vertex}=1$}. This can be thought of as the edge percolation graph of the complete graph $K_{|V|}$.

The average number of edges in such a network scales as,
\begin{align}
|E|_\mathrm{av} = p_\mathrm{edge}\cdot O(|V|^2).	
\end{align}

Some examples are shown in Fig.~\ref{fig:random_graph}.
